Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Allow breaking URLs at hyphens.
https://tex.stackexchange.com/questions/49788/hyperref-url-long-url-with-dashes-wont-break/49791#49791
\hyphenation{Client-Hello}
It was being broken in one case as
	Clien-
	tHello
Restructure for Lantern and Psiphon.

\documentclass{sig-alternate}
\usepackage{txfonts}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{color}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{fronting-diagram}
\caption{
Domain fronting uses different domain names at different layers.
At the plaintext layers visible to the censor---the DNS request and the
TLS Server Name Indication---appears
the front domain \mbox{\textbf{allowed.example}}.
At the HTTP layer, unreadable to the censor,
is the actual destination \mbox{\textbf{forbidden.example}}.
}
\label{fig:fronting}
\end{figure}

@@

Domain fronting works with CDNs because a CDN's frontend server
(called an ``edge server''),
on receiving a request for a resource not already cached,
forwards the request to the domain found in the Host header
(the ``origin server'').
(There are other ways for CDNs to work, but this ``origin pull''
configuration is common.)
% The certificate you get may be that of the front domain,
% or may be a generic shared domain.~\cite{httpsincdn}
Fronting works with Google because Google App Engine, a web application platform,
can host a simple ``reflector'' application that emulates
an origin-pull CDN, simply forwarding every request to another server.
In both cases, the intermediate web service does not forward requests to just anywhere---it
has to be to the domain of a customer.
In order to run a fronting backend,
one generally has to create an account with the web service and pay for bandwidth.

A variation on fronting is ``domainless'' fronting,
in which there is no DNS request and no SNI.
It looks to the censor
like the user is browsing an HTTPS site by its IP address,
or using a web client that does not support SNI.
Domainless fronting can be useful when there is no known front domain
with sufficiently high collateral damage.
The censor is faced with the choice of blocking an entire IP address, not only a domain;
blocking requests without SNI;
or trying to find some other, presumably more expensive, test to distinguish
circumvention traffic.

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as a pluggable transport~\cite{pt} for Tor.
\meek combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received by the server from Tor
are returned to the client within HTTP responses.
\meek's architecture appears in Figure~\ref{fig:meek-architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

\meek has been built into an experimental release of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront
as intermediate web service backends.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:survey} names other fronting-capable services
and Section~\ref{sec:discussion} describes other possible deployments.
\vp{It's confusing here having out-of-order references to sections.  This
also occurs below}
In addition to the Tor pluggable transport,
systems based on \meek are now used by other circumvention systems including
[blinded for anonymous submission].
% ANON
% including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

% \meek is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

Domain fronting and HTTPS address two major circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
Our goal is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than domain blacklists or deep packet inspection---to
force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to traffic analysis
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek
to samples of HTTPS traffic at a network router.

\vp{Seems this should go in the next section instead}
To our knowledge,
the earliest application of domain fronting to circumvention
was by GoAgent~\cite{goagent},
a tool based on App Engine and
once widely used in China.
Fronting has also been used with success since 2013
for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
GoAgent and flash proxy are the systems that most directly
inspire ours.

% We measure the performance...

@@

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
Then a connection is successful, the server can be blacklisted.
Active probing is a precise means of identifying whether a server belongs to a circumvention system,
even when a protocol is hard to detect on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up on observed client connections, to discover
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and obfs4~\cite{obfs4},
described in this section.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each JavaScript-based proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek uses just a few high-value front domains on hard-to-block network infrastructure.
A drawback with flash proxy's use of the browser is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of
domain fronting with App Engine.
\vp{Was it literally an inspiration, or was it concurrent development?
I thought it was more the latter.}
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent does not use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload
\vp{``generally'' upload---what's their practical alternative?}
their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014,
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek over App Engine was similarly affected.
\vp{Add mention of what \meek platforms still worked.}
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
% ANON
% Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
% ANON
% Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
\vp{Explain Pisphon's relevance to meek}

@@

\section{Threat model}

Our threat model includes four actors:
the censor,
the censored client,
the intermediate web service,
and the destination Tor bridge.
\vp{Update this when considering more general services than just
Tor bridges.}
We achieve
circumvention when the client evades the censor to reach
the bridge,
because the bridge can then proxy to anywhere.
The client and bridge cooperate with each other.
The intermediate web service does not need to cooperate with either,
except to the extent that it does not collude with the censor.
% The censor's goal is to prevent circumvention.

\section{Architecture and protocol of meek}
\label{sec:architecture}

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and \mbox{X-Session-Id} headers for classification.
}
\label{fig:protocol}
\end{figure}

\meekserver must handle many clients at once,
and therefore maintains many open connections to a local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that does not work for \meek, for two reasons:
the source IP of the requests is that of the intermediate web service,
not of the actual client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Instead, each client generates a random 256-bit
\vp{it seems like overkill to use 256 bits for this $\ldots$}
session ID for each new Tor stream,
which it sends with its requests in a special
\mbox{X-Session-Id} HTTP header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

@@

As an encrypted tunneling protocol, meek necessarily adds overhead.
Each chunk of data gets an HTTP header, and then the HTTP
request is wrapped in TLS.
We estimate the overhead when meek is used to transport Tor.
Tor uses fixed-size cells of 514 bytes~\cite[\S 0.2]{tor-spec}.
Each cell is wrapped in a TLS Application Data record, which adds 29 bytes
when using a GCM ciphersuite (the default in current versions of Tor).
% (in Tor version~0.2.4.22 using a GCM ciphersuite).
This 543-byte record is received by \meekclient,
which adds an HTTP header whose length is about 400 bytes
\vp{yikes, that's a lot of overhead $\ldots$}
(varying slightly depending on the length of the Host
\vp{It would help to put textual protocol elements in another typeface,
such as \texttt{Host}; you could define a backslash-header macro for this}
field).
The HTTP request goes into its own TLS Application Data record when it becomes HTTPS,
adding about 50~bytes
depending on how much padding is used by the ciphersuite in use.

@@

\section{Camouflage for the TLS layer}
\label{sec:browserextension}

@@

Appropriate TLS camouflage may differ depending on circumstances.
On a traditional desktop PC, using a browser is probably the right choice.
When
[blinded circumvention tool]
\vp{does this need to be blinded?}
% ANON
% Psiphon
ported \meekclient to Android,
they did not use a browser as camouflage,
but rather made all HTTPS requests with the standard Android HTTP API.
This decision makes sense because other Android applications
also use the standard API and share the same TLS fingerprint.

\section{A survey of fronting-capable web services}
\label{sec:survey}

@@

\section{Deployment}
\label{sec:deployment}

% \begin{figure}
% \includegraphics[width=\linewidth]{clients-psiphon3}
% \caption{
% Daily unique users of \meek with
% [blinded circumvention tool]
% % ANON
% % Psiphon
% (note vertical axis).
% The decrease at the end of June
% was caused by an unblocking event that made \meek unnecessary for some users.
% }
% \label{fig:clients-psiphon3}
% \end{figure}

%  &\$49.15 & \$137.98 & \$0.00 & \$187.13 &  \\

% which aggregates statistics reported by Tor relays.
% The number of users is estimated by counting the number
% of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.

>>>>

\documentclass{sig-alternate}
\usepackage{txfonts}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{color}

\hyphenation{Client-Hello}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{fronting-diagram}
\caption{
Domain fronting uses different domain names at different layers.
At the plaintext layers visible to the censor---the DNS request and the
TLS Server Name Indication---appears
the front domain \mbox{\textbf{allowed.example}}.
At the HTTP layer, unreadable to the censor,
is the actual, covert destination \mbox{\textbf{forbidden.example}}.
}
\label{fig:fronting}
\end{figure}

@@

A variation is ``domainless'' fronting,
in which there is no DNS request and no SNI.
It appears to the censor
that the user is browsing an HTTPS site by its IP address,
or using a web client that does not support SNI.
Domainless fronting can be useful when there is no known front domain
with sufficiently high collateral damage;
it leaves the censor the choice of blocking an entire IP address
(or blocking SNI-less requests entirely),
rather than blocking only a single domain.

Domain fronting works with CDNs because a CDN's frontend server
(called an ``edge server''),
on receiving a request for a resource not already cached,
forwards the request to the domain found in the Host header
(the ``origin server'').
(There are other ways CDNs may work, but this ``origin pull''
configuration is common.)
The client issues a request that appears to be destined for
an unrelated front domain, which may be any of the CDN's domains
that resolve to an edge server; this fronted request is what the censor sees.
The edge server decrypts the request,
reads the Host header and
forwards the request to the specified origin,
which in the circumvention scenario is a general-purpose proxy.
The origin server, being a general-purpose proxy, would be blocked by the censor if accessed directly.
Fronting hides its address from the censor.

On services that do not automatically forward requests,
it is usually possible to install a trivial ``reflector'' web application
that emulates an origin-pull CDN.
In this case, fronting does not protect the address of the origin per se;
rather it protects the address of the reflector application,
which in turn forwards requests to the origin.
Google App Engine is an example of such a service:
against a censor that blocks the App Engine domain \urll{appspot.com}
but allows other Google domains,
domain fronting provides access to a reflector running on \urll{appspot.com}.

No matter the specifics of particular web services,
as a general rule they do not forward requests to arbitrary domains---only to domains
belonging to their customers.
In order to deploy a domain-fronting proxy,
one must become a customer of the CDN (or Google, etc.)
and pay for bandwidth.
It is the owner of the covert domain who pays the bandwidth bills,
not the owner of the front domain,
which need not have any relation to the covert domain beyond
using the same web service.

The remainder of this paper is devoted to a deep exploration of
domain fronting as we have deployed it in practice.
Section~\ref{sec:threatmodel} explains our threat model and assumptions.
Section~\ref{sec:related-work} gives general background on the circumvention problem
and outlines its three grand challenges:
address-based blocking, content-based blocking, and active probing.
Domain-fronting systems are capable of meeting all three challenges,
forcing censors to use more expensive, less reliable censorship techniques
that have heretofore not been seen in practice.
Section~\ref{sec:survey} is a summary of CDNs and other services
that are usable for fronting,
identifying general principles as well as
individual idiosyncrasies that affect implementation.
The following sections are case studies of deployment:
Section~\ref{sec:deploy-tor} for Tor,
Section~\ref{sec:deploy-lantern} for Lantern, and
Section~\ref{sec:deploy-psiphon} for Psiphon.
Section~\ref{sec:trafficanalysis} analyzes domain fronting's resistance
to statistical traffic analysis attacks.
Section~\ref{sec:discussion} has general discussion and
Section~\ref{sec:summary} summarizes.

% Circumvention is often presented as an arms race,
% evaders racing to set up proxies before the censor finds and blocks them,
% the censor racing to reverse-engineer the evader's latest technique.
% We submit that a system that comprehensively addresses
% address blocking, content blocking, and active probing---one that
% remains accessible even after the censor knows how it works---occasions
% a qualitative change in the nature of the arms race.
% Deprived of easy DPI, cheap address enumeration, and port scanning for proxies,
% the censor is forced to fall back to more expensive,
% less reliable statistical analysis on traffic flows.
% The domain-fronting systems we describe are the result
% of years of experience with operational
% censorship circumvention systems.
% They are complete, start-to-finish systems designed to defeat
% the capabilities of real-world censors known today.

\section{Threat model}
\label{sec:threatmodel}

Our threat model includes four actors:
the censor,
the censored client,
the intermediate web service,
and the covert destination (some kind of proxy).
We achieve
circumvention when the client evades the censor to reach
the bridge,
because the bridge can then proxy to anywhere.
The client and bridge cooperate with each other.
The intermediate web service does not need to cooperate with either,
except to the extent that it does not collude with the censor.
% The censor's goal is to prevent circumvention.

@@

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
Then a connection is successful, the server can be blacklisted.
Active probing is a precise means of identifying whether a server belongs to a circumvention system,
even when a protocol is hard to detect on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up on observed client connections, to discover
whether a server speaks the Tor protocol.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each JavaScript-based proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek uses just a few high-value front domains on hard-to-block network infrastructure.
A drawback with flash proxy's use of the browser is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

To our knowledge,
the earliest use of domain fronting for circumvention
was by GoAgent~\cite{goagent},
a tool based on App Engine and
once widely used in China.
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent does not use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent upload
their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014,
when all Google services were blocked~\cite{cn-google-block}.
\meek over App Engine was similarly affected.
\vp{Add mention of what \meek platforms still worked.}
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

@@

\section{Fronting-capable web services}
\label{sec:survey}

\section{Deployment on Tor: meek}
\label{sec:deploy-tor}

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01}
is the beginning of a TLSv1.0 ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and \mbox{X-Session-Id} headers for classification.
}
\label{fig:protocol}
\end{figure}

\meekserver must handle many clients at once,
and therefore maintains many open connections to a local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that does not work for \meek, for two reasons:
the source IP of the requests is that of the intermediate web service,
not of the actual client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Instead, each client generates a random 256-bit
session ID for each new Tor stream,
which it sends with its requests in a special
\mbox{X-Session-Id} HTTP header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

@@

As an encrypted tunneling protocol, meek necessarily adds overhead.
Each chunk of data gets an HTTP header, and then the HTTP
request is wrapped in TLS.
We estimate the overhead when meek is used to transport Tor.
Tor uses fixed-size cells of 514 bytes~\cite[\S 0.2]{tor-spec}.
Each cell is wrapped in a TLS Application Data record, which adds 29 bytes
when using a GCM ciphersuite (the default in current versions of Tor).
% (in Tor version~0.2.4.22 using a GCM ciphersuite).
This 543-byte record is received by \meekclient,
which adds an HTTP header whose length is about 400 bytes
(varying slightly depending on the length of the Host
\vp{It would help to put textual protocol elements in another typeface,
such as \texttt{Host}; you could define a backslash-header macro for this}
field).
The HTTP request goes into its own TLS Application Data record when it becomes HTTPS,
adding about 50~bytes
depending on how much padding is used by the ciphersuite in use.

@@

\subsection{Camouflage for the TLS layer}
\label{sec:browserextension}

@@

\section{Deployment on Lantern}
\label{sec:deploy-lantern}

Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.

Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.

enproxy

automated scanner

\section{Deployment on Psiphon}
\label{sec:deploy-psiphon}

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.

Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek with
Psiphon
The decrease at the end of June
was caused by an unblocking event that made \meek unnecessary for some users.
}
\label{fig:clients-psiphon3}
\end{figure}

how clients choose a technique

unfronted mode

users: Figure~\ref{fig:clients-psiphon3}

% Appropriate TLS camouflage may differ depending on circumstances.
% On a traditional desktop PC, using a browser is probably the right choice.
% When Psiphon
% ported \meekclient to Android,
% they did not use a browser as camouflage,
% but rather made all HTTPS requests with the standard Android HTTP API.
% This decision makes sense because other Android applications
% also use the standard API and share the same TLS fingerprint.

@@
